A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-05-13 manuscript/manuscript.tex
Updated FilesetInput to InputFileset

The data specification of a Study class are defined by providing a
list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}).
The lists are collated with data specifications in any base Study
classes during the creation of the class. Input data to the study are
distinguished from derivatives by using the \emph{FilesetInputSpec}
and \emph{FieldInputSpec} subtypes. However, the distinction between
input and derived data is somewhat blurred, as derivative specification
entries can be passed input data when the class is instantiated. In addition,
when subclassing a Study class or aggregating it in a MultiStudy class,
derivative entries can be overridden by input entries, and vice-versa.

@@

While derivatives generated by a Study object are named in accordance
with the data specification of the Study class, input file-sets and fields
do not need specific names when using basic or XNAT
repositories. In these cases, a selection stage matches input data to
entries in the data specification of the Study class. The criteria for
these selections are passed to the
the \emph{inputs} argument of the Study object at instantiation in a
dictionary mapping data specification names to \emph{FilesetInput} and
\emph{FieldInput} objects.

FilesetInput and FieldInput objects are required
to match exactly one fileset or field in every session included in the study.
Matching is typically performed on file
names (dataset labels for XNAT repositories) and field names. If the
names are inconsistent across the study then regular expressions can be
used instead of exact matches with the \emph{pattern} keyword argument.
Additional criteria can be used to distinguish cases where multiple
filesets in the session match the pattern provided, such as DICOM
header values, or the order and ID of the dataset.

>>>>

The data specification of a Study class are defined by providing a
list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}).
The lists are collated with data specifications in any base Study
classes during the creation of the class. Input data to the study are
distinguished from derivatives by using the \emph{InputFilesetSpec}
and \emph{InputFieldSpec} subtypes. However, the distinction between
input and derived data is somewhat blurred, as derivative specification
entries can be passed input data when the class is instantiated. In addition,
when subclassing a Study class or aggregating it in a MultiStudy class,
derivative entries can be overridden by input entries, and vice-versa.

@@

While derivatives generated by a Study object are named in accordance
with the data specification of the Study class, input file-sets and fields
do not need specific names when using basic or XNAT
repositories. In these cases, a selection stage matches input data to
entries in the data specification of the Study class. The criteria for
these selections are passed to the
the \emph{inputs} argument of the Study object at instantiation in a
dictionary mapping data specification names to \emph{InputFileset} and
\emph{InputField} objects.

InputFileset and InputField objects are required
to match exactly one fileset or field in every session included in the study.
Matching is typically performed on file
names (dataset labels for XNAT repositories) and field names. If the
names are inconsistent across the study then regular expressions can be
used instead of exact matches with the \emph{pattern} keyword argument.
Additional criteria can be used to distinguish cases where multiple
filesets in the session match the pattern provided, such as DICOM
header values, or the order and ID of the dataset.
